Explicit Operations on Parametrised Polytopes

### 2018-01-07 dcg-draft.tex
Made some further changes to the proof of Corollary 2

\providecommand{\norm}[1]{\left\|#1\right\|}
\providecommand{\abs}[1]{\left|#1\right|}
\providecommand{\span}{\text{span}}
\providecommand{\conv}{\text{conv}}
\providecommand{\epi}{\text{epi}}
\providecommand{\rk}[1]{\text{rank}\left(#1\right)}

@@

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}
%
We begin by introducing an equivalent characterisation of parametric convexity that provides an insight into the geometrical properties of 
set-valued maps satisfying~\eqref{eq:def:parametrically:convex}.
%
This is based on a description of parametric convexity in terms of conditions on the graph~$\mathscr G(\mathcal W)$ of a set-valued map.
%
\begin{definition}\label{def:graph:of:map}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous set-valued map
such that $\mathcal W(p)$ is convex for all $p\in Y$, then 
%
\begin{equation*}\begin{aligned}
\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
\end{aligned}\end{equation*}
%
denotes the \emph{interior} of its graph and
%
\[
  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \textup{int}(\mathscr G(\mathcal W))
\]
%
its \emph{boundary};
%
\revision{furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{normal cone} is defined as}
%
\[
  \revision{\mathcal N_{\mathcal W} (p,z) = \{\zeta \in\mathbb R^n: \zeta^T (y - z) \leq 0, \;  \forall y\in \mathcal W(p) \} .}
\]
%
\end{definition}
%
\begin{remark}
%
\revision{Note that the normal cone in Definition~\ref{def:graph:of:map} is defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
%
Furthermore, the normal cone $\mathcal N_{\mathcal W} (p,z)$ is the set of normals to all hyperplanes that contain $z$ but no other points in $\mathcal W(p)$.}
%
\end{remark}
%
The central idea connecting parametric convexity of a set valued map $\mathcal W$ with properties of its graph $\mathscr G(\mathcal W)$ is stated next.
%
\begin{theorem}\label{thm:p:convexity:graph}
  \revision{A set-valued map $\mathcal W$ satisfying $\mathcal W(p)\ni 0$ for all $p\in Y$
  is parametrically convex iff
%
\begin{equation}\label{eq:graph:def:p:convexity}
\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \not\in\textup{int} (\mathscr G(\mathcal W))
\end{equation}
%
holds for all $\lambda\in(0,1)$ and all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$ such that  $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$.}
%
\end{theorem}
%
\begin{proof}
  %
  \revision{Consider the set $S$, defined for given $\lambda\in (0,1)$ and $p_1,p_2\in Y$ by
  \[
    S = \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) 
      = \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
  \]
  % \begin{align*}
  %   S &= \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) \\
  %     &= \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
  % \end{align*}
  We first show that $z\in \partial S = S \setminus \textup{int}(S)$ if and only if
  % \begin{equation}\label{eq:Scond}
  %   z = \lambda z_1 + (1 - \lambda) z_2
  %   \quad \text{and} \quad
  %   \mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset 
  % \end{equation}
  $z = \lambda z_1 + (1 - \lambda) z_2$ for some $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ such that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.}

@@

$\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \in\mathrm{int} (\mathscr G(\mathcal W))\vert_{\mathcal C}$ for all $\lambda\in(0,1)$ since

@@

The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
is not parametrically convex for any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.

@@

If $B\neq 0$, then the graph

@@

is convex and violates the conditions of Theorem~\ref{thm:p:convexity:graph}.

>>>>

\providecommand{\norm}[1]{\left\|#1\right\|}
\providecommand{\abs}[1]{\left|#1\right|}
\providecommand{\span}{\text{span}}
\providecommand{\conv}{\text{conv}}
\providecommand{\epi}{\text{epi}}
\providecommand{\rk}[1]{\text{rank}\left(#1\right)}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\interior}{int}
\DeclareMathOperator{\image}{im}

@@

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}
%
We begin by introducing an equivalent characterisation of parametric convexity that provides an insight into the geometrical properties of 
set-valued maps satisfying~\eqref{eq:def:parametrically:convex}.
%
This is based on a description of parametric convexity in terms of conditions on the graph~$\mathscr G(\mathcal W)$ of a set-valued map.
%
\begin{definition}\label{def:graph:of:map}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous set-valued map
such that $\mathcal W(p)$ is convex for all $p\in Y$, then 
%
\begin{equation*}\begin{aligned}
\interior(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
\end{aligned}\end{equation*}
%
denotes the \emph{interior} of its graph and
%
\[
  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \interior(\mathscr G(\mathcal W))
\]
%
its \emph{boundary};
%
\revision{furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{normal cone} is defined as}
%
\[
  \revision{\mathcal N_{\mathcal W} (p,z) = \{\zeta \in\mathbb R^n: \zeta^T (y - z) \leq 0, \;  \forall y\in \mathcal W(p) \} .}
\]
%
\end{definition}
%
\begin{remark}
%
\revision{Note that the normal cone in Definition~\ref{def:graph:of:map} is defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
%
Furthermore, the normal cone $\mathcal N_{\mathcal W} (p,z)$ is the set of normals to all hyperplanes that contain $z$ but no other points in $\mathcal W(p)$.}
%
\end{remark}
%
The central idea connecting parametric convexity of a set valued map $\mathcal W$ with properties of its graph $\mathscr G(\mathcal W)$ is stated next.
%
\begin{theorem}\label{thm:p:convexity:graph}
  \revision{A set-valued map $\mathcal W$ satisfying $\mathcal W(p)\ni 0$ for all $p\in Y$
  is parametrically convex iff
%
\begin{equation}\label{eq:graph:def:p:convexity}
\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \not\in \interior (\mathscr G(\mathcal W))
\end{equation}
%
holds for all $\lambda\in(0,1)$ and all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$ such that  $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$.}
%
\end{theorem}
%
\begin{proof}
  %
  \revision{Consider the set $S$, defined for given $\lambda\in (0,1)$ and $p_1,p_2\in Y$ by
  \[
    S = \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) 
      = \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
  \]
  % \begin{align*}
  %   S &= \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) \\
  %     &= \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
  % \end{align*}
  We first show that $z\in \partial S = S \setminus \interior(S)$ if and only if
  % \begin{equation}\label{eq:Scond}
  %   z = \lambda z_1 + (1 - \lambda) z_2
  %   \quad \text{and} \quad
  %   \mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset 
  % \end{equation}
  $z = \lambda z_1 + (1 - \lambda) z_2$ for some $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ such that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.}

@@

$\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \in\interior (\mathscr G(\mathcal W))\vert_{\mathcal C}$ for all $\lambda\in(0,1)$ since

@@

  \revision{The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
    is  parametrically convex if and only if the matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ is such that $\rank(B) \leq 1$.}
%is not parametrically convex for any $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ such that $\rank (B) >1$.}

@@

\revision{First assume that $B=0$. In this case the graph $\mathscr G(\mathcal W)$ is constant for all $p$, i.e.

@@

which clearly satisfies the  conditions of Theorem~\ref{thm:p:convexity:graph} for parametric convexity.
Next assume $\rank(B)=1$. This implies that the image,  $\image(B)$, of $B$ is one dimensional and in particular there exists $\gamma\in\mathbb{R}^m$ such that $\image(B) = \{\gamma t: t\in\mathbb R\}$.
This implies that the graph $\mathscr G(\mathcal W)$ can be expressed 
  \mathscr G(\mathcal W) = \{(t,z)\in\mathbb R^{1+n}:a_i z\leq c_i-\gamma_i t \; \forall i\in\mathbb N_m\} ,
where $\mathcal W(t)$ is empty for all $t > t^\ast$ for some $t^\ast$ and $\mathcal W(t)$ is a scaled version of $\{ z : Az\leq c\}$ for all $t \leq t^\ast$. Hence the conditions of Theorem~\ref{thm:p:convexity:graph} are again satisfied.}

\revision{Now assume that $\text{rank}(B)=r \geq 1$. In this case
%  $\image(B) = \{\gamma_1t_1+\cdots +\gamma_rt_r : t_1,\ldots,t_r \in \mathbb R\}$ for  some $\gamma_1, \ldots \gamma_r\in\mathbb{R}^m$.
  $\image(B) = \{\Gamma t : t \in \mathbb R^r\}$ for  some $\Gamma \in\mathbb{R}^{m\times r}$,
  and $\mathscr{G}(\mathcal W)$ can be expressed
  \mathscr G(\mathcal W) = \Bigl\{(t,z)\in\mathbb R^{r+n}:a_i z\leq c_i-\sum_{j=1}^r \gamma_{i,j} t_j \; \forall i\in\mathbb N_m\Bigr\},
where $\gamma_{i,j}$ is the $(i,j)$th element of $\Gamma$.
Whenever $\text{rank}(B)\geq 2$ therefore, the graph $\mathscr G(\mathcal W)$ is given by a convex polyhedron that has vertices in the parameter space, which implies that the graph is locally strictly convex and $\mathcal W(p)$ therefore violates Theorem~\ref{thm:p:convexity:graph}.}
